\documentclass[aps
,prstab
%,reprint
%,draft
,preprint,tightenlines
%,linenumbers
%,longbibliography
%,preprintnumbers
%,showpacs
%,showkeys
,amsfonts,amssymb,amsmath
% ,floatfix
]{revtex4-1}

\usepackage{bm}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks=true, allcolors=NavyBlue]{hyperref}

\usepackage{mathptmx}
\linespread{1.1}            
\usepackage[T1]{fontenc}

\setlength{\parindent}{0ex}
\setlength{\parskip}{0.5\baselineskip}

\newcommand{\q}[2]{\ensuremath{#1\ \mathrm{#2}}} % quantity with units
\newcommand{\code}[1]{\textsc{#1}} % computer code
\newcommand{\note}[1]{\emph{\textcolor{red}{#1}}} % note, to-do

% environment for editorial or referee comments
\newenvironment{co}{\em}{}
\newcommand{\bco}{\begin{co}}
\newcommand{\eco}{\end{co}}

% environment for responses
\newenvironment{re}{\color{NavyBlue}}{}
\newcommand{\bre}{\begin{re}}
\newcommand{\ere}{\end{re}}
   
% abbreviations
\newcommand{\kth}{$k$th}
\newcommand{\kthtp}{$k$th-turn pulsing}
\newcommand{\seventhtp}{7th-turn pulsing}
\newcommand{\eighthtp}{8th-turn pulsing}
\newcommand{\tenthtp}{10th-turn pulsing}

\newcommand{\Fma}{Frequency-map analysis}
\newcommand{\fma}{frequency-map analysis}

\begin{document}

Manuscript ZR10120/Fitterer, submitted to Phys. Rev. Accel. Beams  \hfill \today

\section*{Responses to the comments of editors and referees}

Dear Editors,

thank you for the editorial comments and referee reports.

The paper was thoroughly revised, taking those suggestions into account.

Responses to all recommendations and criticisms are reported below.

Best regards,

Giulio Stancari\\
\emph{Corresponding author}\\
\texttt{stancari@fnal.gov}


\section*{Editorial comments}

\bco
We [\ldots] suggest that Reference [5] should be updated to a
journal article:

[5] M. Benedikt, F. Zimmermann, ``Towards future circular colliders,''
Journal of the Korean Physical Society (2016)

and perhaps in addition to include the recent IPAC paper
  
[5b] M. Benedikt and F. Zimmermann, ``FCC: Colliders at the Energy
Frontier,'' Proc. IPAC2018, Vancouver.
\eco

\bre
The references were updated.
\ere

\section*{Problems with manuscript}


\bco In reviewing the figures of your paper, we note that the
  following changes would be needed in order for your figures to
  conform to the style of the Physical Review.  Please check all
  figures for the following problems and make appropriate changes in
  the text of the paper itself wherever needed for consistency.\eco

\begin{description}

\bco
\item[Figure(s) 3, 13, 21, 25, 29] The abbreviation ``a.u.'' is used
  to indicate atomic units only; arbitrary units are abbreviated
  ``arb.  units''; ``A.U.'' is for astronomical units; ``amu'' is for
  atomic mass units.  Please amend your figures and manuscript text
  accordingly.
\eco

\note{(Miriam.)}

\bco
\item[Figure(s) 4] The size and font of the letters and numbers
  appearing in figures should be uniform (or close to it).  Please
  make the letters and numbers more consistent.
\eco

\bre Done.\ere

\bco
\item[Figure(s) 4, 11] Please change E1, E2, etc., to power of 10
  notation (i.e., 10 with appropriate superscript).  We do not print
  computer notation.
\eco

\bre Done for Fig.~4. \ere \note{Miriam, could you please take care of Fig.~11?}

\bco
\item[Figure(s) 9, 10, 16, 23, 26] Please modify quantities so that
  superscripts and subscripts are set as they would appear in
  text. Subscripts should be printed below the line. Also, we do not
  print computer notation. For example, set powers as superscript
  numbers; do not use \verb!^2!, \verb!**2!, etc., for squares of
  quantities. Please adjust the text of the paper accordingly.
\eco

\note{This comment is a bit extreme. Miriam, could you emphasize the
  difference between text and subscripts?}

\bco
\item[Figure(s) 9, 10, 16, 23, 26] The lettering in the axis labels
  and/or numbering size should be increased.
\eco

\note{Miriam.}

\bco
\item[Figure(s) 13, 21, 25, 29] Please rearrange power of 10 in axis
  label for clarity: Either (i)~place the power of 10 as a factor,
  without parentheses, in front of the axis label quantity, changing
  the sign of the power as needed; or (ii)~incorporate the power of 10
  in the topmost or rightmost number on the scale.  Please refer to
  the URL
  \url{http://journals.aps.org/authors/axis-labels-and-scales-on-graphs-h18}
  for a pictorial representation of the preferred forms for axis
  labels.
\eco

\note{Miriam.}

\bco
\item[Figure(s) 23, 26] Please insert post-decimal zeros (1.0, not 1.)
  or delete the decimal point.
\eco

\note{Miriam.}

\end{description}

\bco
TITLE:

This journal does print title footnotes.  Move informatio into your
acknowledgments section.
\eco

\bre Done.\ere

\bco
The following problems were noted in your manuscript.

\begin{itemize}
\item Please check the changes made to the title of your manuscript.
  We propose a modified and somewhat shorter title.
\end{itemize}
\eco

\bre We slightly shortened the title. However, the authors feel that
``active halo control'' is an important concept that should be
emphasized in the title. \ere


\section*{Report of Referee A}

\bco
The paper describes quite extensive simulation and experimental work 
in estimating the effects of either resonant or random dipole 
excitations on the LHC proton beam at injection. Quantities studied 
include beam loss, transverse beam profiles, and bunch length. The 
studies are motivated by the planned use of a hollow electron lens in 
the HL-LHC in pulsed mode (either resonantly with the betatron tune, 
or randomly). The pulsed mode should deplete the beam halo but not 
affect the beam core. 

The paper is well written, with an excellent introduction, high 
quality tables and figure (a few issues are mentioned below), and very 
few typos. It reports in substantial detail on work performed in~2016 
and~2017. 

My main criticism is with the discussion and conclusion. In this 
section, the previous sections are summarized as one would expect, but 
the authors may be able to come to more pronounced conclusions. The 
following sentence is somewhat disappointing after such a large body 
of work: ``However, further work is needed to identify, both in 
simulations and experimentally, candidate excitation patterns that are 
effective for halo removal and that preserve the beam core ...''. 
\eco

\bre We agree that the sentence may sound too weak. We wanted to
stress that this work focuses on core effects, and further studies are
needed on halo removal. The sentence was reworded to emphasize the
conclusions of these studies.  \ere

\bco
Would it be possible, for example, to summarize the beam losses of all
cases studied experimentally and in simulation in a single table? What
conclusions could be drawn from such a direct comparison for the cases
studied? Are any of these excitation pattern viable for a hollow
electron lens in the HL-LHC --- which was the motivation for this work
after all?
\eco

\note{Giulio, Miriam}

\bco
Typos and minor comments: 

\begin{itemize}

\item Table I: ``... for past, present and future colliders.'' Here the 
authors only show the colliders at their labs. The Tevatron is really 
only an example of 3~colliders with comparable stores energy, and the 
ISR (not mentioned at all) had up to several MJ of stored energy too. 

\item Table III: ``\verb!$\mu perv$!'' is not an SI unit. Use 
``\verb!$\mu$\text{AV}^{-2/3}$!''. 

\item Table IV: MOF and MOD are not defined 

\item line 472: ``can thus attributed'' => ``can thus be attributed'' 

\item all figures: Since the paper reports on both measurements and 
simulations it would help the reader if the captions would start with 
either ``Measurement ...'' or ``Simulation of ...'' or ``Calculation of 
...'' 

\item Figure~8: Can ``random'' be a dashed line for better distinction? 
Also, the emittance growth for ``random'' should be calculable (e.g. 
Handbook 1999, Syphers, Sec. 4.5.6 ``Emittance growth''). 

\item Fig.~30, 31: it is difficult to distinguish the symbols for ``damper 
on'' and ``damper off'' 

\item Ref.~[15] --- A better or additional reference may be X.~Gu, PRAB 20, 
023501, 2017. 

\item Ref.~[41] is not used in the text --- there may be more unused 
references 

\item there may be more references on emittance growth --- although I could 
not find a specific one on resonant excitation, as the authors have 
pointed out

\end{itemize}
\eco


\section*{Report of Referee B}

\bco

  In this article various types of beam excitations are numerically
  and experimentally investigated, which act on proton losses, beam
  emittances, and beam distributions in the LHC. These studies are
  important for the design of hollow electron lenses (HEL) for active
  beam halo control of HL-LHC, where a considerable amount of energy
  will be stored in the beam tails.

  Given the need of active halo control for HL-LHC and for future
  high-power accelerators such as HE-LHC and FCC-hh these
  investigations are very essential. The experimental work and
  simulation results presented in this article are excellent. In my
  view, the article contains too many technical details, especially
  too many excitation schemes that lead to confusing plots (see
  Figs.~17, 18, 22, 27, 28 and~32), with many detailed results that
  may not be of great interest for the general audience. This detailed
  information will certainly be very useful for colleagues working on
  high-power hadron colliders and should be complied in a technical
  note or elsewhere. Also in some of the FMA diagrams (see Figs.~9, 10
  and 16) the difference between the various excitation modes are
  barely visible.

  Sometimes plot sizes are just too small and in other cases, the
  difference between various settings seem to be marginal and does not
  contain any further findings.

  Since this work is very relevant for the design and upgrade of
  future high-power hadron accelerators and the performed work is
  excellent, I suggest reducing the length and content of the paper to
  a more compact and comprehensible level. In particular, the number
  of excitation schemes displayed in individual plots should be
  reduced to a level that the content of the various plots is clearly
  recognizable.
\eco

\end{document}
